---
title: "Assignment 4"
output:
  word_document: default
  pdf_document:
    latex_engine: xelatex
  html_notebook: default
always_allow_html: yes
---

```{r setup, include=FALSE}

# This chunk shows/hides the code in your final report. When echo = TRUE, the code
# is shown in the report. When echo = FALSE, the code is hidden from the final report.
# We would like to see your code, so please leave the setting as is during the course.
# This chunk will not show up in your reports, so you can safely ignore its existence.

knitr::opts_chunk$set(echo = TRUE)

```

The following is your first chunk to start with. Remember, you can add chunks using the menu
above (Insert -> R) or using the keyboard shortcut Ctrl+Alt+I. A good practice is to use
different code chunks to answer different questions. You can delete this comment if you like.

Other useful keyboard shortcuts include Alt- for the assignment operator, and Ctrl+Shift+M
for the pipe operator. You can delete these reminders if you don't want them in your report.

```{r}

#setwd("C:\Program Files\R\R-3.6.2")

library("tidyverse")
library("tidymodels")
library("plotly")
library("skimr")
library("caret")
library("lubridate")
library("plyr")
library("dplyr")
library("fpp3")
library("anomalize")

```
# Part 1
# Question 1

```{r}

# 1.a

tsLCOrg <- read_csv("lendingClub.csv")
skim(tsLCOrg)

```
```{r}

# 1.b

tsLCOrg <- as_tsibble(tsLCOrg, index = date, key = state)
tsLCOrg

```
```{r}

# 1.c

summary(tsLCOrg)

```
```{r}

# 1.d

nyei_df <- read_csv("nyEcon.csv")
nyei_df$date <- mdy(nyei_df$date)
nyei_df <- as_tsibble(nyei_df, index = date, key = state)
nyei_df

```
```{r}

# 1.e.i

pop_df <- read_csv("statePop.csv")
tsLCOrg <- inner_join(tsLCOrg, pop_df, by = "state")
tsLCOrg

```
```{r}

# 1.e.ii

tsLCOrg$loansPerCapita <- tsLCOrg$totalLoans/tsLCOrg$`Total population`
tsLCOrg

```
```{r}

# 1.e.iii

tsLC <- left_join(tsLCOrg, nyei_df) %>% 
  as_tsibble(index = date, key = state)

tsLC

```
# Question 2

```{r}

# 2.a

top_10 <- filter(tsLC, tsLC$`Total population` > quantile(tsLC$`Total population`, probs = 0.90))
bottom_10 <- filter(tsLC, tsLC$`Total population` < quantile(tsLC$`Total population`, probs = 0.10))

boxLoansPerCapita_top10 <- top_10 %>%
  ggplot(aes(x = state, y = loansPerCapita)) +
  geom_boxplot() + ggtitle("Top 10th percentile")

boxLoansPerCapita_bottom10 <- bottom_10 %>%
  ggplot(aes(x = state, y = loansPerCapita)) +
  geom_boxplot() + ggtitle("Bottom 10th percentile")

boxLoansPerCapita_top10
boxLoansPerCapita_bottom10

```
```{r}

# 2.b

tsLC_NY <- tsLC %>% 
  filter(state == "NY")

tsLC_NY$avgOpenAcc[which(is.na(tsLC_NY$avgOpenAcc))] <- mean(tsLC_NY$avgOpenAcc, na.rm = TRUE)
tsLC_NY$avgRevolUtil[which(is.na(tsLC_NY$avgRevolUtil))] <- mean(tsLC_NY$avgRevolUtil, na.rm = TRUE)
tsLC_NY$avgTotalAcc[which(is.na(tsLC_NY$avgTotalAcc))] <- mean(tsLC_NY$avgTotalAcc, na.rm = TRUE)

tsLC_NY

```
```{r}

tsLC_CO <- tsLC %>% 
  filter(state == "CO")

tsLC_CO$avgOpenAcc[which(is.na(tsLC_CO$avgOpenAcc))] <- mean(tsLC_CO$avgOpenAcc, na.rm = TRUE)
tsLC_CO$avgRevolUtil[which(is.na(tsLC_CO$avgRevolUtil))] <- mean(tsLC_CO$avgRevolUtil, na.rm = TRUE)
tsLC_CO$avgTotalAcc[which(is.na(tsLC_CO$avgTotalAcc))] <- mean(tsLC_CO$avgTotalAcc, na.rm = TRUE)

tsLC_CO

```
```{r}

tsLC_MA <- tsLC %>% 
  filter(state == "MA")

tsLC_MA$avgOpenAcc[which(is.na(tsLC_MA$avgOpenAcc))] <- mean(tsLC_MA$avgOpenAcc, na.rm = TRUE)
tsLC_MA$avgRevolUtil[which(is.na(tsLC_MA$avgRevolUtil))] <- mean(tsLC_MA$avgRevolUtil, na.rm = TRUE)
tsLC_MA$avgTotalAcc[which(is.na(tsLC_MA$avgTotalAcc))] <- mean(tsLC_MA$avgTotalAcc, na.rm = TRUE)

tsLC_MA

```

```{r}

tsLC_NY %>% 
  time_decompose(loansPerCapita, method = "stl", frequency = "auto", trend = "auto") %>%
  anomalize(remainder, method = "iqr", alpha = 0.05, max_anoms = 0.2) %>%
  plot_anomaly_decomposition()

```
```{r}

tsLC_CO %>% 
  time_decompose(loansPerCapita, method = "stl", frequency = "auto", trend = "auto") %>%
  anomalize(remainder, method = "iqr", alpha = 0.05, max_anoms = 0.2) %>%
  plot_anomaly_decomposition()

```
```{r}

tsLC_MA %>% 
  time_decompose(loansPerCapita, method = "stl", frequency = "auto", trend = "auto") %>%
  anomalize(remainder, method = "iqr", alpha = 0.05, max_anoms = 0.2) %>%
  plot_anomaly_decomposition()

```
```{r}

# 2.c

tsLC_NY$date<- yearmonth(tsLC_NY$date)

tsLC_NY_Decomposed <- tsLC_NY %>%
  select(date, loansPerCapita) %>% 
  model(STL(loansPerCapita ~ trend() + season(window = "periodic"), robust = TRUE)) %>% 
  components() %>%
  autoplot() +
  xlab("Date") + ylab("Loans per capita") +
  ggtitle("Seasonal and Trend decomposition using Loess (STL decomposition)") +
  scale_x_date(date_breaks = "years" , date_labels = "%y")

ggplotly(tsLC_NY_Decomposed)
tsLC_NY_Decomposed

```
```{r}

# 2.d

tsLC_NY_seasonalPlot <- tsLC_NY %>%
  gg_season(loansPerCapita, labels = "both") +
  xlab("Date") + ylab("Loans per capita") +
  ggtitle("Seasonal plot")

tsLC_NY_seasonalPlot

```
```{r}

tsLC_NY_seasonalSubseries <- tsLC_NY %>%
  gg_subseries(loansPerCapita) +
  ylab("Loans per capita") +
  xlab("Date") +
  ggtitle("Seasonal subseries")

tsLC_NY_seasonalSubseries

```
```{r}

# 2.e

tsLC_NY_ACF <- tsLC_NY %>%
  ACF(loansPerCapita, lag_max = 48) %>%
  autoplot() + ggtitle("Autocorrelation function (ACF) plot")

tsLC_NY_ACF

```
```{r}

tsLC_NY_PACF <- tsLC_NY %>%
  PACF(loansPerCapita, lag_max = 48) %>%
  autoplot() + ggtitle("Partial autocorrelation function (ACF) plot")

tsLC_NY_PACF

```

```{r}

# 2.f

tsLC_NY_Lag <- tsLC_NY %>%
  gg_lag(loansPerCapita, lags = c(1, 5, 10, 15, 20, 25), geom = "point") +
  xlab(NULL) + ylab(NULL) +
  ggtitle("Lag plots for loans per capita")

ggplotly(tsLC_NY_Lag)

```
```{r}

# 2.g

library("forecast")

tsLC_NY2 <- tsLC_NY %>% 
  select("date", "loansPerCapita")

autoplot(tsLC_NY2) +
xlab("Year") + ylab("Loans per capita") +
ggtitle("Time series of loans per capita")

```
```{r}

tsLC_NY_ma <- tsLC_NY2 %>%
  mutate(`5-MA` = slide_dbl(loansPerCapita, mean, .size = 5, .align = "center"))

tsLC_NY_ma %>%
  autoplot(loansPerCapita) +
  autolayer(tsLC_NY_ma, `5-MA`, color='red') +
  xlab("Year") + ylab("Loans per capita") +
  ggtitle("Moving average smoothing of loans per capita") +
  guides(colour = guide_legend(title = "series"))

```
# Question 3

```{r}

# 3.a

tsLC_NY_Naive <- tsLC_NY2 %>%
  model(SNAIVE(loansPerCapita)) %>%
  forecast(h = "5 years") %>%
  autoplot(tsLC_NY2, colour = "#769ECB") +
  geom_line(linetype = 'dashed', colour = '#000000') +
  xlab("Year (monthly data)") + ylab("Loans per capita") +
  ggtitle("Naive forecast")

tsLC_NY_Naive

```
```{r}

tsLC_NY_Drift <- tsLC_NY2 %>%
  model(RW(loansPerCapita ~ drift())) %>%
  forecast(h = "5 years") %>%
  autoplot(tsLC_NY2, colour = "#769ECB") +
  geom_line(linetype = 'dashed', colour = '#000000') +
  xlab("Year (monthly data)") + ylab("Loans per capita") +
  ggtitle("Drift forecast")

tsLC_NY_Drift

```
```{r}

# 3.b

fit_tsLC_NY <- tsLC_NY %>%
  model(TSLM(loansPerCapita ~ trend() + season() + avgTerm + avgIntRate + avgAnnualInc + avgVerifStatus + NYCPI + NYUnemployment))

report(fit_tsLC_NY)

```
```{r}

# 3.c

tsLC_NY_Fitted <- augment(fit_tsLC_NY) %>%
  ggplot(aes(x = date)) +
  geom_line(aes(y = loansPerCapita, colour = "Data")) +
  geom_line(aes(y = .fitted, colour = "Fitted")) +
  xlab("Year") + ylab("Loans per capita") +
  ggtitle("Fitted values for loans per capita") +
  scale_x_date(date_breaks = "years" , date_labels = "%y") +
  guides(colour = guide_legend(title = NULL))

ggplotly(tsLC_NY_Fitted)

```
```{r}

fit_tsLC_NY1 <- tsLC_NY %>%
  model(TSLM(loansPerCapita ~ avgTerm + avgIntRate + avgAnnualInc + avgVerifStatus + NYCPI + NYUnemployment))

report(fit_tsLC_NY1)

```
```{r}

tsLC_NY_Fitted1 <- augment(fit_tsLC_NY1) %>%
  ggplot(aes(x = date)) +
  geom_line(aes(y = loansPerCapita, colour = "Data")) +
  geom_line(aes(y = .fitted, colour = "Fitted")) +
  xlab("Year") + ylab("Loans per capita") +
  ggtitle("Fitted values for loans per capita (excluding trend and seasonality") +
  scale_x_date(date_breaks = "years" , date_labels = "%y") +
  guides(colour = guide_legend(title = NULL))

ggplotly(tsLC_NY_Fitted1)

```
```{r}

# 3.d

tsLC_NY_Predicted <- tsLC_NY %>%
  filter(date < "2015-01-01") %>%
  model(TSLM(loansPerCapita ~ trend() + season() + avgTerm + avgIntRate + avgAnnualInc + avgVerifStatus + NYCPI + NYUnemployment)) %>%
  forecast(new_data = tsLC_NY %>% filter(date >= "2015-01-01")) %>%
  autoplot(tsLC_NY, colour = "#960A0A") +
  geom_line(colour = '#535353') +
  xlab("Year") + ylab("Loans per capita") +
  ggtitle("Loans per capita prediction (training pre-2014)")

tsLC_NY_Predicted

```
```{r}

tsLC_NY_Predicted1 <- tsLC_NY %>%
  filter(date < "2016-01-01") %>%
  model(TSLM(loansPerCapita ~ trend() + season() + avgTerm + avgIntRate + avgAnnualInc + avgVerifStatus + NYCPI + NYUnemployment)) %>%
  forecast(new_data = tsLC_NY %>% filter(date >= "2016-01-01")) %>%
  autoplot(tsLC_NY, colour = "#960A0A") +
  geom_line(colour = '#535353') +
  xlab("Year") + ylab("Loans per capita") +
  ggtitle("Loans per capita prediction (training pre-2015)")

tsLC_NY_Predicted1

```
```{r}

# 3.e

fit_tsLC_NY %>% gg_tsresiduals()

```
```{r}

# 3.f

fit_tsLC_NY_ARIMA <- tsLC_NY %>%
  model(fitArima = ARIMA(loansPerCapita ~ PDQ(0,0,0) + avgTerm + avgIntRate + avgAnnualInc + avgVerifStatus + NYCPI + NYUnemployment, stepwise = FALSE, approximation = FALSE))

report(fit_tsLC_NY_ARIMA)

```
```{r}

# 3.g

tsLC_NY %>%
  features(loansPerCapita, unitroot_kpss)

```
```{r}

tsLC_NY %>%
  features(loansPerCapita, unitroot_ndiffs)

```
```{r}

tsLC_NY %>% 
  features(difference(loansPerCapita), unitroot_kpss)

```
```{r}

fit_tsLC_NY_ARIMA1 <- tsLC_NY %>%
  model(fitArima = ARIMA(loansPerCapita ~ PDQ(0,0,0) + pdq(2,1,3) + avgTerm + avgIntRate + avgAnnualInc + avgVerifStatus + NYCPI + NYUnemployment, stepwise = FALSE, approximation = FALSE))

report(fit_tsLC_NY_ARIMA1)

```

# Question 4

```{r}

# 4.a

set.seed(333)
tsLC_NY_Train <- tsLC_NY %>% filter(date < "2016-03-01")
tsLC_NY_Test <- tsLC_NY %>% filter(date >= "2016-03-01")

tsLC_NY_FitAll <- tsLC_NY_Train %>%
  model(
  model1TimeTrendAndSeason = TSLM(loansPerCapita ~ trend() + season()),
  model2_fit_tsLC_NY = TSLM(loansPerCapita ~ trend() + season() + avgTerm + avgIntRate + avgAnnualInc + avgVerifStatus + NYCPI + NYUnemployment),
  model3ArimaGrid = ARIMA(loansPerCapita ~ PDQ(0,0,0), stepwise = FALSE, approximation = FALSE),
  model4fit_tsLC_NY_ARIMA = ARIMA(loansPerCapita ~ PDQ(0,0,0) + avgTerm + avgIntRate + avgAnnualInc + avgVerifStatus + NYCPI + NYUnemployment, stepwise = FALSE, approximation = FALSE))

tsLC_NY_PredictAll <- tsLC_NY_FitAll %>%
  forecast(new_data = tsLC_NY_Test)

accuracy(tsLC_NY_PredictAll, tsLC_NY_Test)

```
```{r}

# 4.b

set.seed(333)
tsLC_NY_Train1 <- tsLC_NY %>% filter(date < "2016-04-01")
tsLC_NY_Test1 <- tsLC_NY %>% filter(date >= "2016-04-01")

tsLC_NY_FitAll1 <- tsLC_NY_Train1 %>%
  model(
  model1TimeTrendAndSeason1 = TSLM(loansPerCapita ~ trend() + season()),
  model2_fit_tsLC_NY1 = TSLM(loansPerCapita ~ trend() + season() + avgTerm + avgIntRate + avgAnnualInc + avgVerifStatus + NYCPI + NYUnemployment),
  model3ArimaGrid1 = ARIMA(loansPerCapita ~ PDQ(0,0,0), stepwise = FALSE, approximation = FALSE),
  model4fit_tsLC_NY_ARIMA1 = ARIMA(loansPerCapita ~ PDQ(0,0,0) + avgTerm + avgIntRate + avgAnnualInc + avgVerifStatus + NYCPI + NYUnemployment, stepwise = FALSE, approximation = FALSE))

tsLC_NY_PredictAll1 <- tsLC_NY_FitAll1 %>%
  forecast(new_data = tsLC_NY_Test1)

accuracy(tsLC_NY_PredictAll1, tsLC_NY_Test1)

```
# Part 2
# Question 1

```{r}

# 1.a

tsRetail <- read_csv("retailSales.csv")
tsRetail$date <- mdy(tsRetail$date)
tsRetail$date<- yearmonth(tsRetail$date)
skim(tsRetail)

```
```{r}

# 1.b

tsRetail <- as_tsibble(tsRetail, index = date)
tsRetail

```
```{r}

# 1.c

autoplot(tsRetail) +
xlab("Year") + ylab("Sales") +
ggtitle("Retail sales over time")

```
```{r}

tsRetail_subset <- tsRetail %>%
  filter(date > "2009-12-31")

autoplot(tsRetail_subset) + 
  xlab("Year") + ylab("Sales") +
  ggtitle("Retail sales over time")

```
# Question 2

```{r}

# 2.a

tsRetail_seasonalPlot <- tsRetail %>%
  filter(date >= "2015-01-01") %>% 
  gg_season(sales, labels = "both") +
  xlab("Year") + ylab("Sales") +
  ggtitle("Seasonal plot")

tsRetail_seasonalPlot

```
```{r}

tsRetail_seasonalSubseries <- tsRetail %>%
  filter(date >= "2015-01-01") %>%
  gg_subseries(sales) +
  ylab("Sales") +
  xlab("Year") +
  ggtitle("Seasonal subseries")

tsRetail_seasonalSubseries

```
```{r}

# 2.b

tsRetail_Decomposed <- tsRetail %>%
  model(STL(sales ~ trend() + season(window = "periodic"), robust = TRUE)) %>% 
  components() %>%
  autoplot() +
  xlab("Year") + ylab("Sales") +
  ggtitle("Seasonal and Trend decomposition using Loess (STL decomposition)") +
  scale_x_date(date_breaks = "years" , date_labels = "%y")

ggplotly(tsRetail_Decomposed)
tsRetail_Decomposed

```
```{r}

tsRetail_Decomposed1 <- tsRetail %>%
  filter(year(date) >= 2005 & year(date) <= 2015) %>% 
  model(STL(sales ~ trend() + season(window = "periodic"), robust = TRUE)) %>% 
  components() %>%
  autoplot() +
  xlab("Year") + ylab("Sales") +
  ggtitle("Seasonal and Trend decomposition using Loess (STL decomposition)") +
  scale_x_date(date_breaks = "years" , date_labels = "%y")

ggplotly(tsRetail_Decomposed1)
tsRetail_Decomposed1

```
```{r}

# 2.c

tsRetail_ACF <- tsRetail %>%
  ACF(sales, lag_max = 48) %>%
  autoplot() + ggtitle("Autocorrelation function (ACF) plot")

tsRetail_ACF

```
```{r}

tsRetail_PACF <- tsRetail %>%
  PACF(sales, lag_max = 48) %>%
  autoplot() + ggtitle("Partial autocorrelation function (ACF) plot")

tsRetail_PACF

```
```{r}

# 2.d

tsRetail_SeasonAdjusted <- tsRetail %>%
  autoplot(sales, color = "blue") +
  autolayer(components(tsRetail %>%
  model(STL(sales))),
  season_adjust, color = "red") +
  xlab("Year") + ylab("Sales") +
  ggtitle("Seasonally adjusted plot")

ggplotly(tsRetail_SeasonAdjusted)

```
```{r}

# 2.e

tsRetail_ma <- tsRetail %>%
  mutate(`2-MA` = slide_dbl(sales, mean, .size = 2, .align = "center-left"))

tsRetail_ma %>%
  autoplot(sales) +
  autolayer(tsRetail_ma, `2-MA`, color='red') +
  xlab("Year") + ylab("Sales") +
  ggtitle("Moving average smoothing of sales") +
  guides(colour = guide_legend(title = "series"))

```
```{r}

tsRetail_ma1 <- tsRetail %>%
  mutate(`12-MA` = slide_dbl(sales, mean, .size = 12, .align = "center-left"))

tsRetail_ma1 %>%
  autoplot(sales) +
  autolayer(tsRetail_ma1, `12-MA`, color='red') +
  xlab("Year") + ylab("Sales") +
  ggtitle("Moving average smoothing of sales") +
  guides(colour = guide_legend(title = "series"))

```

# Question 3

```{r}

# 3.a

fit_tsRetail <- tsRetail %>%
  model(TSLM(sales ~ trend() + season()))

report(fit_tsRetail)

```
```{r}

fit_tsRetail %>% gg_tsresiduals()

```
```{r}

# 3.b

fit_tsRetail_ARIMA <- tsRetail %>%
  model(fitArima = ARIMA(sales ~ PDQ(0,0,0), stepwise = FALSE, approximation = FALSE))

report(fit_tsRetail_ARIMA)

```
```{r}

fit_tsRetail_ARIMA %>% gg_tsresiduals()

```
```{r}

fit_tsRetail_ARIMA1 <- tsRetail %>%
  model(fitArima = ARIMA(sales ~ pdq(4,1,2), stepwise = FALSE, approximation = FALSE))

report(fit_tsRetail_ARIMA1)

```
```{r}

fit_tsRetail_ARIMA1 %>% gg_tsresiduals()

```
```{r}

# 3.c

tsRetail %>% features(sales, unitroot_ndiffs)

```
```{r}

tsRetail %>% features(sales, unitroot_nsdiffs)

```
```{r}

tsRetail_PACF <- tsRetail %>%
  PACF(sales, lag_max = 48) %>%
  autoplot() + ggtitle("Partial autocorrelation function (ACF) plot for sales (before differencing)")

tsRetail_PACF

```
```{r}

tsRetail_DiffPACF <- tsRetail %>%
  mutate(diffSales = difference(difference(sales),12)) %>%
  PACF(diffSales, lag_max = 48) %>%
  autoplot() + ggtitle("Partial autocorrelation function (ACF) plot for sales (after differencing)")

tsRetail_DiffPACF

```
```{r}

# 3.d

set.seed(333)
tsRetail_Train <- tsRetail %>% filter(date < "2011-01-01")
tsRetail_Test <- tsRetail %>% filter(date >= "2011-01-01")

tsRetail_FitAll <- tsRetail_Train %>%
  model(
  model1TimeTrendAndSeason = TSLM(sales ~ trend() + season()),
  model2ArimaGrid = ARIMA(sales ~ PDQ(0,0,0), stepwise = FALSE, approximation = FALSE))

tsRetail_PredictAll <- tsRetail_FitAll %>%
  forecast(new_data = tsRetail_Test)

accuracy(tsRetail_PredictAll, tsRetail_Test)

```
```{r}

# 3.e

set.seed(333)
tsRetail_Train1 <- tsRetail %>% filter(date < "2016-01-01")
tsRetail_Test1 <- tsRetail %>% filter(date >= "2016-01-01")

tsRetail_FitAll1 <- tsRetail_Train1 %>%
  model(
  model1TimeTrendAndSeason1 = TSLM(sales ~ trend() + season()),
  model2ArimaGrid1 = ARIMA(sales ~ PDQ(0,0,0), stepwise = FALSE, approximation = FALSE))

tsRetail_PredictAll1 <- tsRetail_FitAll1 %>%
  forecast(new_data = tsRetail_Test1)

accuracy(tsRetail_PredictAll1, tsRetail_Test1)

```
# Question 4

```{r}

# 4.a

tsRetail1 <- read_csv("retailSales.csv")
tsRetail1$date <- mdy(tsRetail1$date)
tsRetail1 <- as_tsibble(tsRetail1, index = date)

tsRetail1 %>% 
  time_decompose(sales, method = "stl", frequency = "auto", trend = "auto") %>%
  anomalize(remainder, method = "gesd", alpha = 0.05, max_anoms = 0.2) %>%
  plot_anomaly_decomposition()

```
```{r}

# 4.b

tsRetail_Fitted <- augment(tsRetail_FitAll) %>%
  ggplot(aes(x = date)) +
  geom_line(aes(y = sales, colour = "Data")) +
  geom_line(aes(y = .fitted, colour = "Fitted")) +
  xlab("Year") + ylab("Sales") +
  ggtitle("Fitted values for sales") +
  scale_x_date(date_breaks = "years", date_labels = "%y") +
  guides(colour = guide_legend(title = NULL))

ggplotly(tsRetail_Fitted)

```
```{r}

tsRetail_Fitted1 <- augment(tsRetail_FitAll1) %>%
  filter(date > "2010-01-01") %>% 
  ggplot(aes(x = date)) +
  geom_line(aes(y = sales, colour = "Data")) +
  geom_line(aes(y = .fitted, colour = "Fitted")) +
  xlab("Year") + ylab("Sales") +
  ggtitle("Fitted values for sales") +
  scale_x_date(date_breaks = "years", date_labels = "%y") +
  guides(colour = guide_legend(title = NULL))

ggplotly(tsRetail_Fitted1)

```
# Bonus questions

```{r}

# 1.

usEcon_df <- read_csv("usEcon.csv")
usEcon_df$date <- mdy(usEcon_df$date)
usEcon_df <- as_tsibble(usEcon_df, index = date)
usEcon_df

```
```{r}

tsRetail_usEcon <- left_join(tsRetail, usEcon_df, by = c("date" = "date"), all = TRUE)
tsRetail_usEcon <- as_tsibble(tsRetail_usEcon,index = date)
tsRetail_usEcon

```
```{r}

set.seed(333)
tsRetail_usEcon_Train <- tsRetail_usEcon %>% filter(date < "2011-01-01")
tsRetail_usEcon_Test <- tsRetail_usEcon %>% filter(date >= "2011-01-01")

tsRetail_usEcon_FitAll <- tsRetail_usEcon_Train %>%
  model(tsRetail_usEcon_TimeTrendAndSeason = TSLM(sales ~ trend() + season() + income + unemployment + CPI + inflation))

report(tsRetail_usEcon_FitAll)

```


